The Impact of Malaria Episodes and Treatment Regimens on Adverse Pregnancy Outcomes in Ugandan Women

### 2025-02-26 products/manuscript/Manuscript.qmd
New Folder

# 1. Summary/Abstract

@@

# 2. Introduction

## 2.1 General Background Information

@@

## 2.1.1 Description of data and data source

@@

## 2.1.2 Questions/Hypotheses to be addressed

@@

# 3. Methods

#

@@

## 3.1 Data aquisition

@@

## 3.2 Data import and cleaning

@@

## 3.3 Statistical analysis

# 3.3.0.1 Exploratory/Descriptive analyses

@@

*Logistic and Count Regression Analyses (Maternal Health Outcomes)* This section examines the relationship between malaria episodes during pregnancy and adverse outcomes like preterm birth and stillbirth. The exposure variable will be the total number of malaria episodes during pregnancy, with preterm birth and stillbirth as binary outcomes. Logistic regression will assess these associations, adjusting for confounders such as maternal age, parity, and socioeconomic status. Another analysis will investigate whether treatment type (SP vs. DP) reduces malaria episodes. Here, the exposure variable will be treatment, and the outcome will be the total number of malaria episodes. Poisson or negative binomial regression will be used to compare episode counts across treatment groups, adjusting for factors like baseline malaria status, geographic region, and seasonal variations.

*Chi-Square Tests and Logistic Regression (Infant Health Outcomes)* This section focuses on birth weight, gestational age, and neonatal mortality outcomes. First, we will assess whether infants born to mothers treated with DP are less likely to have low birth weight compared to those treated with SP. A chi-square test will initially compare proportions, followed by logistic regression to adjust for confounders such as maternal nutrition and gestational age. Next, neonatal mortality will be compared between treatment groups using chi-square tests for unadjusted differences, with logistic regression models controlling for factors such as birth complications, preterm birth, and birth weight. Lastly, we will examine whether malaria infection rates during pregnancy are associated with low birth weight and preterm birth. Logistic regression models will be used for this analysis, adjusting for maternal age, parity, and gestational age.

*Logistic Regression and Chi-Square Tests (Malaria and Pregnancy Outcomes)* This section will assess whether placental malaria is associated with preterm birth and low birth weight. Logistic regression models will evaluate these associations while adjusting for relevant confounders, such as the number of malaria episodes during pregnancy and maternal health variables. Additionally, the difference in placental malaria prevalence between SP and DP treatment groups will be examined using chi-square tests for initial comparisons and logistic regression for adjustments, controlling for factors like the number of malaria episodes and regional differences.

@@

# 4. Results

## 4.1 Exploratory/Descriptive analysis

@@

## 4.2 Basic statistical analysis

@@

## 4.3 Full analysis

@@

# 5. Discussion

>>>>

# Summary/Abstract

@@

# Introduction

## General Background Information

@@

## Description of data and data source

@@

## Questions/Hypotheses to be addressed

@@

# Methods

@@

## Data aquisition

@@

## Data import and cleaning

@@

## Statistical analysis

# Exploratory/Descriptive analyses

@@

Logistic and Count Regression Analyses (Maternal Health Outcomes)

This section examines the relationship between malaria episodes during pregnancy and adverse outcomes like preterm birth and stillbirth. The exposure variable will be the total number of malaria episodes during pregnancy, with preterm birth and stillbirth as binary outcomes. Logistic regression will assess these associations, adjusting for confounders such as maternal age, parity, and socioeconomic status. Another analysis will investigate whether treatment type (SP vs. DP) reduces malaria episodes. Here, the exposure variable will be treatment, and the outcome will be the total number of malaria episodes. Poisson or negative binomial regression will be used to compare episode counts across treatment groups, adjusting for factors like baseline malaria status, geographic region, and seasonal variations.

Chi-Square Tests and Logistic Regression (Infant Health Outcomes)

This section focuses on birth weight, gestational age, and neonatal mortality outcomes. First, we will assess whether infants born to mothers treated with DP are less likely to have low birth weight compared to those treated with SP. A chi-square test will initially compare proportions, followed by logistic regression to adjust for confounders such as maternal nutrition and gestational age. Next, neonatal mortality will be compared between treatment groups using chi-square tests for unadjusted differences, with logistic regression models controlling for factors such as birth complications, preterm birth, and birth weight. Lastly, we will examine whether malaria infection rates during pregnancy are associated with low birth weight and preterm birth. Logistic regression models will be used for this analysis, adjusting for maternal age, parity, and gestational age.

Logistic Regression and Chi-Square Tests (Malaria and Pregnancy Outcomes)

This section will assess whether placental malaria is associated with preterm birth and low birth weight. Logistic regression models will evaluate these associations while adjusting for relevant confounders, such as the number of malaria episodes during pregnancy and maternal health variables. Additionally, the difference in placental malaria prevalence between SP and DP treatment groups will be examined using chi-square tests for initial comparisons and logistic regression for adjustments, controlling for factors like the number of malaria episodes and regional differences.

@@

# Results

## Exploratory/Descriptive analysis

@@

## Basic statistical analysis

@@

## Full analysis

@@

# Discussion
